\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Vedant Modi} \\ \vspace{1pt}
    \small 832-963-0248 $|$ \href{mailto:vedant@vedantmodi.com}{\underline{vedant@vedantmodi.com}} $|$ 
    \href{https://www.vedantmodi.com}{\underline{vedantmodi.com}} $|$
    \href{https://github.com/thevedantmodi}{\underline{github.com/thevedantmodi}} $|$
    \href{https://www.linkedin.com/in/thevedantmodi}{\underline{linkedin.com/in/thevedantmodi}}
    
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Tufts University}{Aug. 2022 -- May 2026}
      {GPA 3.82, BS Computer Science, BA Applied Mathematics}{Somerville, MA}
      \resumeSubSubheading{Relevant Coursework: Machine structure and Assembly programming, Data structures and algorithms}{}
      \resumeSubSubheading{Mathematical proofs, Artificial intelligence, Linear algebra}{}{}{}
  \resumeSubHeadingListEnd

% REMOVE HERE FOR ONE PAGE
% \resumeSubHeadingListStart
%     \resumeSubheading
%       {Carnegie Vanguard High School}{Aug. 2018 – May 2022}
%       {GPA 4.70 / 4.00}{Houston, TX}
%       \resumeSubSubheading{Significant Activities: International Thespian Society, National Honor Society, Interact}{}
%   \resumeSubHeadingListEnd
% END REMOVE


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Tufts JumboCode}{September 2023 – Present}
      {Developer}{Somerville, MA}
      \resumeItemListStart
        \resumeItem{Develop an app benefiting the Emerald Necklace Conservancy educating visitors on preservation.}
        \resumeItem{Design a full-stack web application using React, MongoDB, Bun.}
        \resumeItem{Practice team-based coding powered by Git and GitHub collaboration tools.}
      \resumeItemListEnd

      \resumeSubheading
      {Tufts University, Department of Computer Science}{May 2023 – Present}
      {Course Assistant for Data Structures and Algorithms}{Somerville, MA}
      \resumeItemListStart
        \resumeItem{Host office hours aiding students in course projects and lecture topics.}
        \resumeItem{Grade student assignments by studying submissions for functionality, testing, and course coding standards.}
        \resumeItem{Contribute to a program that organizes course grading. Built as a Python CLI mimicking a SQL database.}
      \resumeItemListEnd

% REMOVE HERE FOR ONE PAGE
      \resumeSubheading
      {Tufts University, Office of Academic Space Management}{May 2023 – Present}
      {Receptionist}{Somerville, MA}
      \resumeItemListStart
        \resumeItem{Help community via organizing mail, and analyzing building usage for largest academic buildings on campus.}
      \resumeItemListEnd
% END REMOVE

    \resumeSubheading
      {Texas Heart Institute}{May 2021 – Aug. 2021}
      {Visual Communications Intern}{Houston, TX}
      \resumeItemListStart
        \resumeItem{Designed graphics and created animations representing cardiological research for publicity.}
        \resumeItem{Interviewed for animation work by the \textit{Houston Chronicle}.}
    \resumeItemListEnd

% REMOVE HERE FOR ONE PAGE
      % \resumeSubheading
      % {Carnegie Theatre Company}{Aug. 2018 – May 2022}
      % {Webmaster, Media Designer}{Houston, TX}
      % \resumeItemListStart
      %   \resumeItem{Maintained website, social media, ticket sales, and production marketing graphics.}
      %   \resumeItem{Designed live projections, edited videos, and rigged lights for productions.}
      %   \resumeItem{Recognized by the International Thespian Society for work on theatrical marketing.}
      % \resumeItemListEnd
% END REMOVE

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Relevant Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{World Clock} $|$ \emph{JavaScript, HTML, CSS}}{Aug. 2023}
          \resumeItemListStart
            \resumeItem{Created a web application showing the time of chosen cities, with a helpful interactive map to aid in visualization.}
            \resumeItem{Published application to personal website with custom autocomplete search bar and tracked development with Git.}
            \resumeItem{Designed using Maptiler and OpenStreetMap for map, and modeled UI with Figma.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{JetLag} $|$ \emph{Python}}{Mar. 2023 – Present}
          \resumeItemListStart
            \resumeItem{Constructed a tool to aid sleeptime changes when traveling between timezones during air travel,
            given flight details (e.g. airports, departure and arrival
            times).}
            % TODO Fix this point 
            \resumeItem{Used Python \texttt{tz} library in conjunction with database of
            IATA-recognised airports to parse user input for calculations.}
          \resumeItemListEnd
  
      % GAMING, WEBDEV
      % \resumeProjectHeading{}{}
      % \resumeProjectHeading
      %     {\textbf{IATA Guesser} $|$ \emph{JavaScript, HTML, CSS}}{Jul. 2023}
      %     \resumeItemListStart
      %       \resumeItem{Memory game generating random IATA airport codes for the user to recall}
      %       \resumeItem{Used Toastr for popups reflecting answer and created a custom autocomplete search box}
      %     \resumeItemListEnd

      % DATA SCIENCE
      % \resumeProjectHeading
      %     {\textbf{IATA Country Sorter} $|$ \emph{Python}}{Jul. 2023}
      %     \resumeItemListStart
      %       \resumeItem{Invented a sorting script that maps inputted IATA airport codes into an output file for their country.}
      %       \resumeItem{Used for searching for flights by country in ITA Matrix}
      %     \resumeItemListEnd

      % ALGOS
      \resumeProjectHeading
          {\textbf{gerp} $|$ \emph{C++, Makefile, Bash}}{Apr. 2023 – May 2023}
          \resumeItemListStart
            \resumeItem{Built a program with partner that searches for user-queried text from specified directory.}
            \resumeItem{Designed with dictionary ADT, where dictionary stores words and filepath, and shared via Git.}
          \resumeItemListEnd
          \resumeProjectHeading
          {\textbf{zap} $|$ \emph{C++, Makefile, Bash}}{Apr. 2023}
          \resumeItemListStart
          \resumeItem{Wrote a Huffman compressor/decompressor for text files and practiced using priority queue ADT and recursion.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: C/C++, Python, JavaScript, TypeScript, HTML/CSS, R, SQL, LaTeX} \\
     \textbf{Frameworks and Environments}{: React, React Native, Node.js, MongoDB, Bun} \\
     \textbf{Developer Tools}{: Visual Studio Code, Git, GitHub, Makefile, Figma, Unix, Bash, SFTP, SSH, AutoHotkey (Windows)} \\
     \textbf{APIs and Libraries}{: LeafletJS, OpenStreetMap, Maptiler, Maplibre, Mapbox, ArcGIS, OpenSkyNetwork, pandas} \\
     \textbf{Media}{: Droneography, Photoshop, Lightroom, After Effects, Davinci Resolve Studio, Premiere Pro, InDesign, Wordpress} \\
     \textbf{Spoken Languages}{: Proficiency in English, Hindi, Spanish, and French} \\
     \textbf{Woodworking}{: Proficiency in power tooling like sawing (miter, table, band) and drilling}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}