\resumeSubheading
{Software Engineering Intern – Markets Technology, Commercial \& Investment
Banking}{June 2025 – August 2025}
{J.P. Morgan Chase \& Co.}{New York, NY}
\resumeItemListStart
\vspace{1mm} 

% TODO: mention SDLC, navigating business critical times like code freezes


\resumeItem{Built end-to-end and deployed production monitoring application for high
touch bond trading platform, enabling performance analytics across \textbf{5
critical data enrichment services} for over \textbf{100,000+ trades per day} and
improving trade execution in global markets. Flagged \textbf{20\% of requests}
suffering extreme latency in key service, driving target optimizations that
significantly improved trade execution workflow. }

\resumeItem{Expanded scope of product ownership by iterating on features and
incorporating feedback from stakeholders in \textbf{5+ widespread locations}.
Enhanced the application to provide actionable metrics for \textbf{99\% of
requests}, iterated on live troubleshooting features, and ultimately achieved
\textbf{100\% alignment with the product vision}.}

\resumeItem{Demonstrated product proficiency and facilitated product improvements
by delivering a live presentation of the application to \textbf{teams
across 20+ locations}, including senior executives and key stakeholders, resulting in
actionable feedback, effectively showcasing the tool's utility, and providing
technical points of improvement for line of business. }

\resumeItem{Brought application from concept to completion \textbf{within 10
weeks} using the firm SDLC; managing feature development, testing, stakeholder
approval, and critical business periods such as code freezes. Enabled future
work within the SDLC by creating a maintainable and well-documented codebase.}

\resumeItem{Prototyped an AI-powered travel recommendation tool later adopted by
firm, leveraging an agentic RAG workflow to give detailed user suggestions and
promotional feedback. Recognized among \textbf{the top 5 teams} in New York City
offices for effective presentation and innovative product.}

\resumeItem{Proactively expanded domain knowledge within \textbf{2 weeks} by attending learning sessions, organizing regular coffee chats with experienced developers and management, and studying technical documentation to accelerate project progress.}
% \resumeItem{Optimized trading platform latency by developing a suite of services that asynchronously 
% listen to and aggregate data from multiple data pipelines, reducing bottlenecks and improving
% real-time information delivery to high-frequency traders.} 



% \resumeItem{Recognized as \textbf{top 5 hackathon team
% among 2000+ teams} for building an AI-powered travel recommendation tool and marketing assistant by
% leveraging an agentic RAG workflow to give detailed user suggestions and promotional feedback.}
\resumeItemListEnd

% created a project that monitored peformance across multiple services in bonds
% high touch trading platform.
% Helps find how well services are meeting performance thresholds, identify
% issues quickly in services, or improve service resiliency.
% Performance focused -- trades update multiple times within a second
% successfully shipped application to production
% collaborated with global stakeholders to action upon feedback given by them to
% improve the tool
% 